### 2021-07-22 PrevAdjSurvey.tex
Updates from Overleaf

%\usepackage{algorithm}
%\usepackage{fancyhdr}
\usepackage{graphics,color,pict2e}
\usepackage{epsfig}
%\usepackage{times}
%\usepackage[cmbold]{mathtime}
%\usepackage{bm}
%\usepackage{rotating}
%\usepackage{pdflscape}
%\usepackage{longtable}

@@

Another way to address this problem is to assume that $X_i \sim Poisson( n_i \theta_i)$ and use the methods 
of \citet{FayF:1997} or \citet{FayK:2017}. This should give a confidence interval for $\beta=\sum_{i=1}^{k} w_i \theta_i$ 
that gives a lower and upper confidence distribution that is distributed gamma. (I will let you work out those details. Let me know if it is not easy.)

>>>>

%\usepackage{algorithm}
%\usepackage{fancyhdr}
\usepackage{graphics,color,pict2e}
\usepackage{epsfig}
%\usepackage{times}
%\usepackage[cmbold]{mathtime}
%\usepackage{bm}
%\usepackage{rotating}
%\usepackage{pdflscape}
%\usepackage{longtable}
\usepackage{booktabs}

@@

Another way to address this problem is to assume that $X_i \sim Poisson( n_i \theta_i)$ and use the methods
of \citet{FayF:1997} or \citet{FayK:2017}.
The notation is different in those papers. Here is the correspondence between the notations in these notes and in \citet{FayK:2017}.

\begin{tabular}{cc}
These Notes & Fay and Kim  \\ \hline
$w_i$     & $s_i$ \\
$\theta_i$ & $\lambda_i$ \
\end{tabular}

and $X_i$ and $n_i$ are the same in both papers.

This should give a confidence interval for $\beta=\sum_{i=1}^{k} w_i \theta_i$
that gives a lower and upper confidence distribution that is distributed gamma. (I will let you work out those details. Let me know if it is not easy.)

\subsection{Current Results}

For this section I have applied 4 methods to 2 populations, with 10,0000 replications each.

\noindent Methods:
\begin{itemize}
    \item AC \& AC\_adj: The Agresti-Coull and Agresti-Coull adjusted methods for survey samples described in \cite{Dean:2015}. Implemented by hand.
    \item wspoissonTest \& wspoissonTest\_midp: the methods described in \cite{FayF:1997} and \cite{FayK:2017}. Implemented in \cite{asht}.
\end{itemize}

In each scenario, I use the 2020 census population counts for all states \& DC and specify the exact number of cases in each state's population to achieve an overall prevalence $\approx$  0.5\%.
Per \cite{Lemeshow1985SurveysTM}, I implement a 2-stage sampling algorithm, where $m$ states are sampled with replacement and $\tilde{n}$ people are sampled from each of the $m$ states.
In the results here, $m = 12,000$ and $\tilde{n} = 1$, equivalent to a simple random sample from the country.
Alternative schemes like $m = 120$ and $\tilde{n} = 100$ seem to produce worse results for the wspoissonTest methods, but I have not investigated this fully.\\
The differences between the two scenarios are presented below.\\

\noindent Scenarios:
\begin{itemize}
    \item few\_state: California, Texas, Florida, and New York each have 1.5\% prevalence, while all other states have no cases.
    \item many\_state: all states have 0.5\% prevalence
\end{itemize}

\noindent Results:
\begin{table}[h]
\centering
\begin{tabular}{llrrr}
\toprule
scenario & method & coverage & lower\_error\_freq & upper\_error\_freq\\
\midrule
few\_state & AC & 0.9570 & 0.0259 & 0.0171\\
few\_state & AC\_adj & 0.9570 & 0.0259 & 0.0171\\
few\_state & wspoissonTest & 0.9629 & 0.0216 & 0.0155\\
few\_state & wspoissonTest\_midp & 0.9559 & 0.0250 & 0.0191\\
\addlinespace
many\_state & AC & 0.9515 & 0.0287 & 0.0198\\
many\_state & AC\_adj & 0.9515 & 0.0287 & 0.0198\\
many\_state & wspoissonTest & 0.9597 & 0.0246 & 0.0157\\
many\_state & wspoissonTest\_midp & 0.9517 & 0.0281 & 0.0202\\
\bottomrule
\end{tabular}
\end{table}

I have not found any scenarios that ``break" the AC methods, which appear to be on par with the wspoissonTest\_midp methods.
